\bf The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-03-04 paper/forestecology.Rmd
more formatting

---
title: "The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees"

# to produce blinded version set to 1 and change blinded <- TRUE on line 54 below
blinded: 0

authors: 
- name: Albert Y. Kim 
  affiliation: Program in Statistical & Data Sciences, Smith College
  thanks: "Assistant Professor, Statistical & Data Sciences, Smith College, Northampton, MA 01063 (e-mail: akim04@smith.edu)."

- name: David N. Allen
  affiliation: Biology Department, Middlebury College

- name: Simon P. Couch
  affiliation: Mathematics Department, Reed College

@@

keywords:
- forest ecology, inter-species competition, tree growth, R, Rstats, tidyverse, sf, cross-validation, spatial statistics

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace}
- \linenumbers
---

@@

- Run full simulation on SCBI data
- run time considerations

@@

A.Y.K. and D.N.A. conceived the ideas and coded most of the package in the early design stages. A.Y.K. led the writing of the manuscript. S.P.C. refactored much of the package's code in the later design stages to align with R and "tidy" programming best practices [@wickham_welcome_2019]. All authors contributed critically to the drafts and gave final approval for publication.

>>>>

---
title: The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

blinded: 0

authors: 
- name: Albert Y. Kim 
  affiliation: Program in Statistical & Data Sciences, Smith College
  thanks: "Assistant Professor, Statistical & Data Sciences, Smith College, Northampton, MA 01063 (e-mail: akim04@smith.edu)."
- name: David N. Allen
  affiliation: Biology Department, Middlebury College
- name: Simon P. Couch
  affiliation: Mathematics Department, Reed College

@@

keywords:
- forest ecology, competition, tree growth, R, tidyverse, sf, cross-validation, spatial statistics

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace, fancyhdr}
# Add line numbers:
- \linenumbers
# Add running header:
- \pagestyle{fancy}
- \fancyhead[LO,LE]{forestecology R package}
- \renewcommand{\sectionmark}[1]{\markright{#1}{}}
---

@@

@@

AYK and DNA conceived the ideas and coded most of the package in the early design stages. AYK led the writing of the manuscript. SPC refactored much of the package's code in the later design stages to align with R and "tidy" programming best practices [@wickham_welcome_2019]. All authors contributed critically to the drafts and gave final approval for publication.

### 2021-03-04 paper/forestecology.tex
more formatting

\usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace}
\linenumbers

@@

\noindent%
{\it Keywords:} forest ecology, inter-species competition, tree growth, R, Rstats,
tidyverse, sf, cross-validation, spatial statistics
\vfill

@@

\begin{itemize}
\tightlist
\item
  Run full simulation on SCBI data
\item
  run time considerations
\end{itemize}

@@

A.Y.K. and D.N.A. conceived the ideas and coded most of the package in
the early design stages. A.Y.K. led the writing of the manuscript.
S.P.C. refactored much of the package's code in the later design stages
to align with R and ``tidy'' programming best practices
\citep{wickham_welcome_2019}. All authors contributed critically to the
drafts and gave final approval for publication.

>>>>

\usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace, fancyhdr}
\linenumbers
\pagestyle{fancy}
\fancyhead[LO,LE]{forestecology R package}
\renewcommand{\sectionmark}[1]{\markright{#1}{}}

@@

\noindent%
{\it Keywords:} forest ecology, competition, tree growth, R, tidyverse, sf,
cross-validation, spatial statistics
\vfill

@@

@@

AYK and DNA conceived the ideas and coded most of the package in the
early design stages. AYK led the writing of the manuscript. SPC
refactored much of the package's code in the later design stages to
align with R and ``tidy'' programming best practices
\citep{wickham_welcome_2019}. All authors contributed critically to the
drafts and gave final approval for publication.
